### 2025-01-28 paper/icml25/first/sects/background.tex
clarify some notion

\subsection{Markov Decision Processes}
To provide context for our work, we first introduce the reinforcement learning (RL) framework. 
Particularly, we focus on multi-agent settings, where multiple agents interact with each other and the environment.
In doing so, each task is then modeled as a partially observable, decentralized, finite-horizon, Markov Decision Process (MDP)~\cite{Shapley53}, $\mdp$: $(\agents,\states,\allo,\alla,\allp, \allr, \transition, \horizon, \discount, \initdist)$. Where $\agents=[\na]$ and $\states$ denote the set of agents and the state space, respectively. $\allo={\{\observations{i}\}}_{i\in\agents}$ and $\alla={\{\actions{i}\}}_{i\in\agents}$ are the observation space and action space for each agent. ${\{\stateobs{i}:\states\rightarrow\observations{i}\}}_{i\in\agents}$ are the projections from the state to the observation space and ${\{\rewards{i}:\states\times\actions{i}\times\states\rightarrow\mathbb{R}\}}_{i\in\agents}$ are the reward functions for each agent. $\transition:\states\times\alla\rightarrow\states$ denotes the transition function. $\discount$ and $\horizon$ denote the discount factor and the time horizon respectively. Finally, $\initdist$ is the initial state distribution.

Further, let us denote denote the space of trajectories, $\trajectories = {\left(\states\times\alla\times\states\times\mathbb{R}^{n}\right)}^*$, where each trajectory consists of a sequence of: starting state, action per agent, subsequent state, and reward per agent. Given a generic trajectory $\tau\in\trajectories$, we denote its $i$-th starting state with $s_i^\tau$, its $i$-th action for agent $j$ with $a_{ij}^\tau$, and its $i$-th reward for agent $j$ with $r_{ij}^\tau$.

>>>>

\subsection{Markov Decision Processes}
To provide context for our work, we first introduce the reinforcement learning (RL) framework. 
Particularly, we focus on multi-agent settings, where multiple agents interact with each other and the environment.
In doing so, each task is then modeled as a partially observable, decentralized, finite-horizon, Markov Decision Process (MDP)~\cite{Shapley53}, $\mdp$: $(\agents,\states,\allo,\alla,\allp, \allr, \transition, \horizon, \discount, \initdist)$. Where $\agents=\{1, 2, \dots, \na\}=[\na]$ and $\states$ denote the set of agents and the state space, respectively. $\allo={\{\observations{i}\}}_{i\in\agents}$ and $\alla={\{\actions{i}\}}_{i\in\agents}$ are the observation space and action space for each agent. ${\{\stateobs{i}:\states\rightarrow\observations{i}\}}_{i\in\agents}$ are the projections from the state to the observation space and ${\{\rewards{i}:\states\times\actions{i}\times\states\rightarrow\mathbb{R}\}}_{i\in\agents}$ are the reward functions for each agent. $\transition:\states\times\alla\rightarrow\states$ denotes the transition function. $\discount$ and $\horizon$ denote the discount factor and the time horizon respectively. Finally, $\initdist$ is the initial state distribution.

Further, let us denote the space of trajectories, $\trajectories = {\left(\states\times\alla\times\states\times\mathbb{R}^{n}\right)}^*$, where each trajectory consists of a sequence of: starting state, action per agent, subsequent state, and reward per agent. Given a generic trajectory $\tau\in\trajectories$, we denote its $i$-th starting state with $s_i^\tau$, its $i$-th action for agent $j$ with $a_{ij}^\tau$, and its $i$-th reward for agent $j$ with $r_{ij}^\tau$.
